NILPOTENT INVARIANTS \\ FOR GENERIC DISCRETE SERIES OF REAL GROUPS

### 2025-03-07 whittaker_JIMJ.tex
Typographical trick, now 21 pages

\subsubsection{Involutions}~
 In our setting we may view $G(\R)$ as the fixed-point group $G^\sigma$, where $\sigma$ is an anti-holomorphic involution~$\sigma$ of~$G$ such that $G(\R) = G^\sigma$. Fix such an involution~$\sigma$, and choose a compatible Cartan involution~$\theta$ for $G$. This means:
$\theta$ is an algebraic involution, commuting with~$\sigma$,
and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$ and $K(\R)=G(\R)^\theta=K^\sigma$.
Set $\g=\Lie(G)$, and let $\s$ be the $(-1)$-eigenspace of~$\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions. Set $\g(\R)=\Lie(G(\R))$.

@@

Suppose $\pi$ is an irreducible admissible representation of $G(\R)$  on a Hilbert space. 
The underlying
$(\g,K)$-module is on the space of $K$-finite vectors in
$V$; we will denote it by~$\pi_K$.

Conversely, if $\pi$ is an irreducible $(\g,K)$-module, it can be
realized as the $K$-finite vectors of a Hilbert space representation, which we
refer to as the Hilbert space globalization of~$\pi$.

@@

The proof of Lemma~\ref{lem:iso_q} uses Galois cohomology for the compact real form.  Recall $\theta\sigma = \sigma\theta$, and $G^{\sigma\theta}$ is a compact real form of~$G$. 
The involutions $\sigma$ and $\theta$ coincide on~$G^{\sigma\theta}$,
therefore  $H^1(\sigma, G^{\sigma\theta})$ and  $H^1(\theta, G^{\sigma\theta})$ are the same set,
which we will denote by  $H(\ast, G^{\sigma\theta})$.
Now the inclusion $G^{\sigma\theta} \hookrightarrow G$ induces canonical maps 
\begin{equation} \label{bij_cohom} H^{1}(\sigma,  G) \longleftarrow H(\ast, G^{\sigma\theta}) \longrightarrow H^{1}(\theta,  G).\end{equation}
By \cite[Corollary~4.4 and Corollary 4.7]{galois}, both of these maps are \emph{bijections}.
Replacing~$G$ by~$Z$ we get bijections $H^{1}(\sigma, Z) \leftarrow H(\ast, Z^{\sigma\theta}) \rightarrow H^{1}_{\theta}(\Gamma, Z)$.
These fit with the bijections~\eqref{bij_cohom} into a commutative diagram
\[
\begin{CD}
H^{1}(\sigma, Z) @<<< H^1(\ast, Z^{\sigma\theta})@>>> H^{1}(\theta, Z)
 \\
@V{\varphi_{\sigma}}VV @VVV @V{\varphi_{\theta}}VV  \\
H^{1}(\sigma, G) @<<< H^1(\ast, G^{\sigma\theta})@>>> H^{1}(\theta,  G)
\end{CD}
\]
where $\varphi_\sigma$, $\varphi_\theta$ are the maps in \eqref{interp_q_cohomology}.

@@

In this section only we need to  choose a particular an isomorphism \mbox{$\gder\simeq \gder^*$}.
For this we let $\kappa$ be the killing form, and define $\psi_\kappa:\gder\rightarrow \gder^*$ by
$$
\psi_\kappa(X)(Y)=\kappa(X,Y)\quad (X,Y\in \gder).
$$

@@

>>>>

\subsubsection{Involutions}~
 In our setting we may view $G(\R)$ as the fixed-point group $G^\sigma$, where $\sigma$ is an anti-holomorphic involution~$\sigma$ of~$G$. Fix such an involution~$\sigma$, and choose a compatible Cartan involution~$\theta$ for $G$. This means:
$\theta$ is an algebraic involution, commuting with~$\sigma$,
and $G(\R)^\theta$ is a maximal compact subgroup of~$G(\R)$. Set $K=G^\theta$ and $K(\R)=G(\R)^\theta=K^\sigma$.
Set $\g=\Lie(G)$, and let $\s$ be the $(-1)$-eigenspace of~$\theta$ acting on~$\g$, where we use the notation $\sigma, \theta$ also for the automorphisms of~$\g$ induced by the above involutions. Set $\g(\R)=\Lie(G(\R))$.

@@

Suppose $\pi$ is an irreducible admissible representation of $G(\R)$  on a Hilbert space. 
The underlying
$(\g,K)$-module is on the space of $K$-finite vectors in
$V$; we will denote it by~$\pi_K$. 
Conversely, if $\pi$ is an irreducible $(\g,K)$-module, it can be
realized as the $K$-finite vectors of a Hilbert space representation, which we
refer to as the Hilbert space globalization of~$\pi$.

@@

The proof of the Lemma uses Galois cohomology for the compact real form.  Recall $\theta\sigma = \sigma\theta$, and $G^{\sigma\theta}$ is a compact real form of~$G$. 
The involutions $\sigma$ and $\theta$ coincide on~$G^{\sigma\theta}$,
therefore  $H^1(\sigma, G^{\sigma\theta})$ and  $H^1(\theta, G^{\sigma\theta})$ are the same set,
which we will denote by  $H(\ast, G^{\sigma\theta})$.
Now the inclusion $G^{\sigma\theta} \hookrightarrow G$ induces canonical maps 
\begin{equation} \label{bij_cohom} H^{1}(\sigma,  G) \longleftarrow H(\ast, G^{\sigma\theta}) \longrightarrow H^{1}(\theta,  G).\end{equation}
By \cite[Corollary~4.4 and Corollary 4.7]{galois}, both of these maps are \emph{bijections}.
Replacing~$G$ by~$Z$ we get bijections $H^{1}(\sigma, Z) \leftarrow H(\ast, Z^{\sigma\theta}) \rightarrow H^{1}_{\theta}(\Gamma, Z)$.
These fit with the bijections~\eqref{bij_cohom} into a commutative diagram
\[
\begin{CD}
H^{1}(\sigma, Z) @<<< H^1(\ast, Z^{\sigma\theta})@>>> H^{1}(\theta, Z)
 \\
@V{\varphi_{\sigma}}VV @VVV @V{\varphi_{\theta}}VV  \\
H^{1}(\sigma, G) @<<< H^1(\ast, G^{\sigma\theta})@>>> H^{1}(\theta,  G)
\end{CD}
\]
where $\varphi_\sigma$, $\varphi_\theta$ are the maps in \eqref{interp_q_cohomology}.

@@

In this section only we need to  choose a particular an isomorphism \mbox{$\gder\simeq \gder^*$}.
For this we let $\kappa$ be the Killing form, and define $\psi_\kappa:\gder\rightarrow \gder^*$ by
$$
\psi_\kappa(X)(Y)=\kappa(X,Y)\quad (X,Y\in \gder).
$$

@@

\small
